\LARGE \bf Multi-Camera Visual Servoing of a Flapping Wing Micro Air Vehicle

### 2012-09-12 manuscript.tex
Updates to MAV platform and control sections. - Added guesses to platform parameters - Added control equations and explanations

%----------------------------------------------------------------------------%
\subsection{Flapping Wing Micro Air Vehicle}
%TODO(humphrey)
The flying platform used in this experiment is the H2Bird flapping wing MAV. It features a X-wing clap-fling flapping design, with a brushed DC motor powering the wings for propulsion and a tail propeller and servo-controlled tail elevator for control. Onboard electronics include a 40 MIPS microprocessor, 6 DoF IMU, 802.15.4 radio, VGA camera, and motor drivers powered by a 90 mAh lithium polymer battery. In routine flight, the H2Bird achieves [insert speed] m/s ground speed and can operate for approximately [10] minutes.

@@

%----------------------------------------------------------------------------%
\subsection{MAV Internal Control}
%TODO(humphrey)
Due to the high pitch angles experienced by the IBird, a quaternion representation of vehicle pose was chosen to avoid Euler angle singularities. A quaternion-based controller as used in was adapted to control the iBird thrust, yaw, and pitch actuators. Given a reference attitude q, the error qe is dened as the rotation required to reach the reference from the current pose. The components of the error quaternion are then linearized to produce body axis angular errors. Control of the pitch and yaw axes is handled by three PID loops commanding the wing thrust, elevator, and tail prop. This independent PID loop architecture was chosen for simplicity in tuning and implementation, as well as acceptable performance in the absence of a system model. The iBird currently does not have a roll actuator, but our current control scheme has sufficed for the reference tracking in this work.

>>>>

%----------------------------------------------------------------------------%
\subsection{Flapping Wing Micro Air Vehicle}
%TODO(humphrey)
The flying platform used in this experiment is the H2Bird flapping wing MAV. Built around the Silverlit I-Bird RC flyer powertrain and clap-fling wings, the H2Bird has a wingspan of [40?] cm and weighs [14?] grams fully loaded. A tail propeller and servo-controlled tail elevator provide control in the yaw and pitch axes. An onboard electronics package combines a 40 MIPS microprocessor, 6 DoF IMU, 802.15.4 radio, VGA camera, and motor drivers with a 90 mAh lithium polymer battery for autonomous flight. In routine flight, the H2Bird averages [insert speed] m/s ground speed and can operate for approximately [10] minutes.

@@

%----------------------------------------------------------------------------%
\subsection{MAV Onboard Control}
%TODO(humphrey)
Rudimentary attitude control for the H2Bird runs onboard, estimating pose by naively integrating the IMU and depending on PID for control. The simplistic nature of our state estimation and control is due to the stringent resource constraints applied by the platform.

A quaternion representation of vehicle pose was chosen to avoid Euler angle singularities. This choice of pose representation also lends itself well to remote guidance, as relative body and world coordinate angular displacements can be represented compactly with quaternion multiplication.

Given a reference attitude $q$, the error $q_e$ is defined as the rotation required to reach the reference from the current pose. The components of the error quaternion are then linearized to produce body axis angular errors. Control of the pitch and yaw axes is handled by three PID loops commanding the wing thrust, elevator, and tail prop.

\begin{equation}
\label{quat_error}
q_e = q'\otimes q_r
\end{equation}

\begin{equation}
\label{quat_angle}
\alpha = 2acos(q_{e,w})
\end{equation}

\begin{equation}
\label{quat_linearize}
Q_e = \alpha*q_e/sin(\alpha /2)
\end{equation}
